Robustness of MinD oscillation in \emph{Escherichia coli} with diverse cell shapes

### 2014-08-29 paper/paper.tex
edited text in Mannik section and adjusted size of paper/plot-arrow Tested everything on quipu.

\section{Comparison of Mannik's Experimental and Our Stadium Shapes}
We have made and studied different types of plots and movies that show
the change in concentration of MinD over time. We have found that the
deterministic simulations of the protein reaction sequence discussed
above results in robust oscillatory behavoir of polar selection and
oscillation in a wide variety of cell shapes.  This differs with
Mannik's experimental findings that show much less regular behavoir,
with a large variation in the location of maxima.  On the other hand,
our stochastic simulations show irregular behavoir in the irregular
shapes and more regular, pole to pole oscillations in the pill and
stadium shaped cells, agreeing well with Mannik's experimental
findings.

Figure~{arrow-pill-stadium} and Figure~{randst-plot-ave} show color
plots of time-averaged MinD overlayed by arrows depicting sequential
maxima that are global in space and local in time.  Our shapes that
designed to look like Mannik cells show well the inadequacy of the
deterministic method of simulation and conversely the accuracy of the
stochastic method.  The stochastic method movies (and arrow plots of
Figure~{randst-plot-ave}) show irregular location of maxima that is
similar to what is observed experimentally by Mannik. There is a
general bias towards back and forth behavoir, which can be seen in the
box plots of Figure~{box-mannik}, but the behavoir is irregular and
the location of the maxima vary a significant amount.  On the other
hand, the deterministic simulations show behavoir that is much too
regular, exhibiting locations of maxima that do not vary.  The
deterministic method is seen to be inadequate.

@@

Judging that at this point that we have a fair idea of how our two
methods compare in terms of experimental acuracy, we are intersted to
investigate the limits of the break down of regular activity, by
simulating large, regular, 'stadium' shapes.  These shapes have the
flattened, pancake like form of our irregularly shaped cells, but from
the top down they look as pills do. In two dimensions they are
composed of a rectangle with two half ellipse connected on either end.
They are also made to have a large volume similar to the Mannik
shapes.

>>>>

\section{Comparison of Mannik's Experimental and Our Stadium Shapes}
We have made and studied plots and movies of the MinD in a number of
simulated cell shapes and sizes. We have found that the deterministic
simulations of the protein reaction sequence discussed above results
in robust oscillatory behavoir of polar selection and oscillation in
not only symmetrical shapes, such as the wild type pill shape, but
also in very assymetrical, flatttened cells, such as those studied by
Mannik.  This differs with Mannik's experimental findings that show
much less regular behavoir, with a large variation in the location of
maxima.  On the other hand, our stochastic simulations show both
irregular behavoir in the assymetrical shapes and more regular, pole
to pole oscillations in the symmetric pill and stadium shaped cells,
agreeing well with Mannik's experimental findings.

Figure~{arrow-pill-stadium} and Figure~{randst-plot-ave} show color
plots of time-averaged MinD overlayed by arrows depicting sequential
maxima that are global in space and local in time.  Our shapes that
are designed to look like Mannik cells show well the inadequacy of the
deterministic method of simulation and conversely the accuracy of the
stochastic method.  Our stochastic method movies (and arrow plots of
Figure~{randst-plot-ave}) show irregular location of maxima that is
similar to what is observed experimentally by Mannik. There is a
general bias towards back and forth behavoir, which can be seen in the
box plots of Figure~{box-mannik}, but the behavoir is irregular and
the location of the maxima vary a significant amount.  On the other
hand, the deterministic simulations show behavoir that is much too
regular when compared with experiment, exhibiting locations of maxima
that do not vary.  The deterministic method is seen to be inadequate.

@@

Judging that at this point that we have a fair idea of how our two
methods compare in terms of experimental acuracy, we are interested to
investigate the limits of the break down of regular activity, by
simulating large, regular, 'stadium' shapes.  These shapes have the
flattened, pancake like form of the assymetric cells, but from the top
down they look as pills do. In two dimensions they are composed of a
rectangle with two half ellipse connected on either end.  They are
also made to have a large volume that is similar to the Mannik shapes.
